\tool: Revisiting BadUSB with Type-C

### 2021-03-07 WOOT/Files/conclusion.tex
responsible disclosure fixed

As future work, we will further explore the potential of \textit{isolated UI
rendering} and implement it on a customized operating system. Moreover, we also
hope to lower the power consumption for network transmission in \tool to make
it more practical.

\section{Responsive Disclosure}

Responsive disclosure have already been carried out, we have already contacted the affected vendors through proper channel and are waiting for mitigation being deployed.

>>>>

As for future work, we will further explore the potential of \textit{isolated UI
rendering} and implement it on a customized operating system. Moreover, we also
hope to lower the power consumption for network transmission in \tool to make
it more practical.

\section{Responsible Disclosure}

Responsible disclosure have already been carried out, we have already contacted Huawei and Apple through proper channel and are waiting for mitigation being deployed. By now, we have already heard from Huawei PSIRT who has already been analyzing this security issue while Apple has not responded yet.
